---
title: "3_DP_CatiaReis"
author: "Cátia Reis"
date: "12/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PRACTICAL 3 - DATA
## Built-in R dataset

In the following code-chunk, I load the built-in R dataset called "Titanic" in which we find information about passengers who have survived the Titanic :
```{r}
data("Titanic")
summary(Titanic)
```
```{r}
str(Titanic)
```

In the R output (see above), we see that there are four variables which are all character
There are four variables in this data set :


**R data types.** There are four CHARACTER variables in this data set : 

  1. Class: 1st, 2nd, 3rd, crew
  2. Sex: Male, Female
  3. Age: Child, Adult
  4. Survived: No, yes

**Statistical data types.** These four variables are called NOMINAL QUALITATIVE variables. I hesitated to say that the "class" variable was *ordinal* because of the sequence "1st, 2nd, 3rd" but "crew" didn't quite fit in this. 


## External dataset 

Here, I load the dataset called "skate_soundtrack_data" which includes data on the **skate soundtracks**.
```{r}
library(readr)
data_skate <- read.csv("https://raw.githubusercontent.com/the-pudding/data/master/skate-music/soundtrack_data.csv")
str(data_skate)
head(data_skate)
```

There are seven variables but the author of the data set says that the "genre_fake" column should be ignored as they used it for "testing purposes". 

There are three INTEGER variables (R data type is given first, statistical type is given after the colon in the bullet list :

- tote : quantitative discrete
- year : qualitative
- id : qualitative

The remaining variables are character variables :

- artist : qualitative nominal
- group : qualitative nominal
- genre_fake : qualitative nominal
- genre : qualitative nominal

```{r}
library(dplyr)
new_skate<-data_skate %>%
select(artist, year,tote)
```

We can see that the Beatles was the most played band in 2008 in skate videos from the skatevideo website. <!--verify--> 





