---
title: "3_DP_CatiaReis"
author: "Cátia Reis"
date: "12/03/2022"
output: 
  github_document:
    toc: true
bibliography: referencesDP3.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Practical - Week 3

```{r, message= F , warning= F}
library(dslabs)
```

### Dataset 1 - Built-in R dataset

In the following code-chunk, I load the built-in R dataset called "Titanic" in which we find basic information about passengers who have survived the Titanic :

```{r}
data(Titanic)
```

```{r}
str(Titanic)
```

In the R output (see above), we see that there are four CHARACTER variables in this data set :  

  1. Class: 1st, 2nd, 3rd, crew
  2. Sex: Male, Female
  3. Age: Child, Adult
  4. Survived: No, yes

**Statistical data types.** These four variables are called NOMINAL QUALITATIVE variables. I hesitated to say that the "class" variable was *ordinal* because of the sequence "1st, 2nd, 3rd" but "crew" didn't quite fit in this. 

### Data set 2 - External dataset 

Here, I load the dataset called "skate_soundtrack_data" done by @misc which includes data on **skate soundtracks** used in skateboarding videos. 

```{r}
library(readr)
data_skate <- read.csv("https://raw.githubusercontent.com/the-pudding/data/master/skate-music/soundtrack_data.csv")
str(data_skate)
head(data_skate)
```

There are seven variables but the author of the data set says that the "genre_fake" column should be ignored as they used it for "testing purposes". <!-- cite source --> 

There are three INTEGER variables (R data type is given first, statistical type is given after the colon in the bullet list :

- tote : quantitative discrete
- year : qualitative
- id : qualitative

The remaining variables are character variables :

- artist : qualitative nominal
- group : qualitative nominal
- genre_fake : qualitative nominal
- genre : qualitative nominal

### Dataset 3 - Dataset from dslabs package

Same old, same old, looking at the type of variables we find in the 'movielens' dataset. 
```{r}
str(movielens)
```
Out of 7 variables (and I say this with the voice of a loto presenter) we have...: <!-- change?-->

- Four integers : movieId, year, userId, timestamp
- One character variable: title
- One factor : genres
- One numerical : rating. 

The most important variables for this dataset are probably "title" and "rating" which are respectively a "qualitative" and "quantitative ordinal" variable. 

```{r}
head(movielens)
```













