---
title: "DP_Week4"
author: "Cátia Reis"
date: "06/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data practical 4

```{r , message=F, warning=F}
library(readr)
library(dplyr)
library(datasets)
library(dslabs)
library(gapminder)
```

<!-- * Filter the data by two variables -- e.g., countries of your choice -- and save the results to a new data frame -->
```{r}
skate <- read.csv("https://raw.githubusercontent.com/the-pudding/data/master/skate-music/soundtrack_data.csv")
```

Now, let's filter the skate dataset to look at "Electronic" music with a total of uses in the videos that is equal or superior to 20.
```{r}
skate_filter<-skate %>% filter(genre=="Electronic",tote>=10)
skate_filter
```

I am happy to announce that M83 is in fourth place of the most used electronic music in skate videos.  



Since there are a couple of columns we do not really care about, let's select those that matter. 

```{r}
skate_selected <- skate_filter %>% select(artist,tote,genre,year)
```

In the following code, the first rows are displayed. 
```{r}
head(skate_selected)
```


Now, we can find the last rows. 
```{r}
tail(skate_selected)
```

Here, you can see the structure of the dataset. 
```{r}
str(skate_selected)
```

Now, let's arrange our data. It will show the rows ordered by "tote" from the lowest to the highest value.

```{r}
skate_arranged<-skate_selected %>% arrange(desc(tote,genre))
skate_arranged
```

We can see that the most popular electronic artist is Sol. 

<!--Describe any patterns or lack of patterns that you see in the data (note: you can also rearrange the data in other ways if that helps, but look at it and write up in a sentence or two your findings)-->


In the following code chunk, I decided to take the initial dataset to see the total of times each genre was used in skate videos. 
```{r}
total<-skate %>% group_by(genre) %>% summarize(total_use_of_genre=sum(tote)) %>% arrange(desc(total_use_of_genre))
```

```{r}
any(is.na(skate))
```


If there were NA values in my dataset and I would want to exclude them, I would use "filter(!is.na(name_of_colum_where_there_are_NA))". But as we have seen with the previous formula. 



We are going to join the following two datasets.


```{r}
full_join(results_us_election_2016,murders)
```
<!-- describe relationship -->







