---
title: "week8_DP"
author: "Cátia Reis"
date: "13/04/2022"
output: 
  github_document:
  toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Paper plane experiment
```{r message=F, warning=F}
library(dplyr)
library(ggplot2)
```
### The dataset 

We will be looking at the same dataset that we used in [week 6](DP_week6/DP_week6.md). 

```{r}
coordination<-read.table(file="coordination.csv", header=TRUE, sep=";",dec=",") 
```

#### Reminder 

In this experiment, we used a paper plane task to understand if face-to-face interaction had an impact on learning performance. We had a **non-interactive condition** where one participant learned to do a paper plane by themselves by watching a youtube video tutorial. Then, this same participant taught another participant how to do the paper plane and this constituted our **interactive condition**. In the dataset, you can see that there is a "roles" column with two options (teacher,student). The teacher stands for the non-interactive condition while the student stands for the interactive condition data. We measured learning performance by looking at the distance and time the paper planes did. Finally, we also coded what we consider "feedbacks". We considered that the more feedbacks you had in a student-teacher pair, the more interactive the pair was. Thus, we also hypothesized that the more interactive a pair was, the better the performance of the student's plane would be. 

- Explanatory variables (as named in the dataset) : "roles" and "feedback_percentage" 
- Response variables : performance, i.e. "average_flying_time"& "average_distance"

### Correlation

```{r}
cor.test(coordination$feedback_percentage,coordination$average_flying_time)
cor.test(coordination$feedback_percentage,coordination$average_distance)
```
There is a positive correlation between the two and the p-value is below 0.05 which tells us it is significant. Correlation does not imply causation. 

Now fit your model in a (General) Linear Model (remember the assumptions)

```{r}
general<-lm(coordination$feedback_percentage~coordination$average_distance)
summary(general)
```

```{r}
general<-glm(coordination$feedback_percentage~coordination$average_distance)
summary(general)
```

#### Linear model functions
```{r}
general<-lm(coordination$feedback_percentage~coordination$average_flying_time)
summary(general)
```
#### Plot with linear model

```{r}
ggplot(coordination,aes(feedback_percentage,average_flying_time,label=rownames(coordination),color=roles)) +
    geom_point() + labs(y ="Average flying time (in seconds)" , x = "Feedback percentage") + geom_text(hjust = -0.3)+geom_smooth(method = "lm", se = TRUE,color="black")  
```


