---
title: "DP_week7"
author: "Cátia Reis"
date: "06/04/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message= F, warning=F}
library(ggplot2)
library(dplyr)
```

## Boybands 
```{r}
boyband<-read.csv("https://raw.githubusercontent.com/the-pudding/data/master/boybands/boys.csv")
str(boyband)
head(boyband)
```

There are only character variables except "height" which is integer. They are all qualitative nominal while the former is quantitative discrete. In this dataset you find the "name" of each band member, the name of the band and then physical characteristics of the members such as "facial_hair" or which "accessories" they have along with their "eyes" color, and other ones. 

### Visualizing 

Our data has some blank spaces, let's make it clearer for R that there are NAs. 

```{r}
boyband1 <- boyband %>% mutate_all(na_if,"")
```

Now that we've cleared the blanks, let's see what our data tells us. Since we have quite a lot of variables, let's look at the hair styles found in the different bands.  
```{r}
ggplot(boyband1,aes(y=band))+geom_bar(aes(fill=hair_style)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Wow! That's quite a lot of hair styles. 

###  Statistics

[Cool statistics song](https://youtu.be/BvWefB4NGGI?t=22)

#### Hypotheses

- **H1** : Members from the same boyband are more likely to have the same hair style. 
- **H0** : Pertaining to a certain boyband has no impact on your hair style. 

#### Statistical test

```{r}
chisq.test(boyband1$band,boyband1$hair_style)
```
#### ohter
```{r}

qplot(x = band, y = height, data = boyband, geom = "boxplot", fill = band) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  theme(legend.position="none")
```

