---
title: "DP_week7"
author: "Cátia Reis"
date: "06/04/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message= F, warning=F}
library(ggplot2)
```

## Boybands 
```{r}
boyband<-read.csv("https://raw.githubusercontent.com/the-pudding/data/master/boybands/boys.csv")
str(boyband)
head(boyband)
```

There are only character variables except "height" which is integer. They are all qualitative nominal while the former is quantitative discrete. In this dataset you find the "name" of each band member, the name of the band and then physical characteristics of the members such as "facial_hair" or which "accessories" they have along with their "eyes" color, and other ones. 

### Visualizing 

Let's take the binary variable "hair_frosted" because that is very funny to me. 

```{r}
ggplot(boyband, aes(x = height)) +  geom_bar()
```
We see we have an odd plot since we didn't really clean our data. There are empty cells. Still, we see that the majority of band members do not have frosted hair. 


###  Statistics

[Cool statistics song](https://youtu.be/BvWefB4NGGI?t=22)

#### Hypothesis

This might not be the most interesting idea of hypothesis, but I wonder, I can only think of Justin Timberlake's spaghetti hair. 

Is hair frosting impacted by boys' hair color? 

#### Statistical test

```{r}
lm_1<-lm(height ~ band  , data = boyband)
summary(lm_1)
```


```{r}

qplot(x = band, y = height, data = boyband, geom = "boxplot", fill = band) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  theme(legend.position="none")
```


